Concordance between observations and simulations in the evolution of the mass relation between supermassive black holes and their host galaxies

### 2022-04-25 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
Merger with Aklant and John's edit

\section{Introduction} \label{sec:intro}
The close correlations between \red{the mass of} supermassive black holes (\red{\mbh}) and the properties of their host galaxies (e.g., stellar mass\red{, \smass}) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}. To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over \red{cosmic time}. While, an {\it observed} evolution has been found \red{since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15, Ding2020, 2021arXiv210902751L} in} which the growth of BHs predates that of the host, other studies \red{\citep[e.g.,][]{Schramm2013, Sun2015} predict that} BHs grow commensurately with galaxies.
However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009}.

@@

To avoid any potential biases related to the selection of the quasars, \citet{2021arXiv210902751L} isolated 877 sources which are uniformly selected based on their PSF-magnitudes, color cuts using single-epoch SDSS photometry and the value of the measured \smass. Specifically, we use the {\it ugri} color-selected sample (228 sources) from SDSS I/II~\citep{Richards2002}, and the CORE sample from SDSS BOSS (408 sources) and eBOSS (241 sources) surveys~\citep{Ross2013, Myers2015} (hereafter the uniform sample). These samples are initially selected based on PSF-magnitude cuts of $15 < i < 19.1$ (for {\it ugri}), and $i > 17.8$ and $g, r < 22.0$ (for CORE). Furthermore, a limit on \smass\ is set to assure the detection of the host, especially since the rate and accuracy of detection is higher when \smass\ is increasing, resulting in a final sample of 646 quasars. These selections will be adopted in an equivalent manner to the simulated samples to mitigate selection effects thus allowing the fair comparison.

@@

The measurements of the \mbh-\smass\ relations for both the HST and HSC samples are obtained with a consistent approach. Thus, we expect the measurement errors of these two samples to be at a comparable level (i.e., $\Delta$\mbh$=0.4~$dex, $\Delta$\smass$=0.2~$dex). 
Indeed, the two samples are consistent with a lack of evolution in the mass ratio~\citep[see Figure 6 of][]{2021arXiv210902751L}, even though the sample selection is slightly different.

\begin{deluxetable*}{lccccc}
\tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} & MBII & Illustris &  TNG100 & TNG300 & Horizon-AGN
}
\startdata
box sizes $(\mathrm{cMpc})^3$  & $142.7^3$ & $(106.5)^3$ & $(111)^3$ & $(302)^3$ & $(142)^3$ \\
particles  & $2\times1792^3$ & $2\times1820^3$ & $2\times1820^3$ & $2\times2500^3$ & $\sim2\times1024^3$ \\
\cline{1-6}
{\bf mass resolution} \\
 dark matter &$1.57\times10^7$ & $6.26\times10^6$ & $7.5\times10^6$ & $5.9\times10^7$ & $8\times10^7$ \\
 baryonic matter &$3.14\times10^6$ & $1.26\times10^6$ & $1.4\times10^6$ & $1.1\times10^7$ & $2\times10^6$ \\
\cline{1-6}
{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ \red{radiative efficiency})} \\
High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
Low acc. mode  & -- & 0.35 $\times$ 0.2 & $\leq0.2 \times$ 0.2 & $\leq0.2 \times$ 0.2 & 1 $\times$ 0.1 \\
Transitions btw. modes & -- & 0.05 & \multicolumn{2}{c}{min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%]} & 0.01 \\
\cline{1-6}
AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & $\dot{M}_{Bondi}$&$\dot{M}_{Bondi}$ & $\alpha\dot{M}_{Bondi}$ \\
maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
\enddata
\tablecomments{In the penultimate row, $\alpha$ is the boost factor. For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$[(\rho/\rho_0)^2, 1]$. $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$. \todo{Aklant: The $\leq$ sign in the low accretion feedback mode of TNG is also not clear. Is it a fixed value or a distribution?} \todo{Aklant: Referee asks us whether the same radiative efficiency is used to compute AGN luminosity in all the simulations. But we already show these values in Table 1, which are different, don't we?} \aklant{\bf{Yes the radiative efficiencies are different in the different simulations, and we use these different values for the computing the luminosities in each case. This is true at least for the simulations that I provided to you.}}
}
\end{deluxetable*}

\section{Simulations and comparison strategy}
\todo{Uniform the descriptions of the simulations to lack homogeneity. (Illustris has star formation threshold). Re-write the section and provide the same information}
\label{sec:simulations}
We introduce the simulation samples that are adopted in this section. All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation (see Section~\ref{subsec:SAM}). In Table~\ref{tab:sim_sum}, we summarized the key elements for each hydrodynamic simulation being considered.

\red{Note that each simulation adopt either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} IMF. To make a self-consistent comparison, we ensure that the adopted IMF for both the simulation and the observation are the same. The assumed IMF is needed to obtain the mass-to-light ratio and convert the observed luminosity to stellar mass to perform the comparison. For numerical simulation, the mass is the base material which is IMF independent.}

\subsection{{\tt MassiveBlackII} (MBII)}\label{subsec:MBII}
MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $(142.7~\mathrm{cMpc})^3$
and $2\times1792^3$ particles. \todo{Aklant: Please answer what is the factor 2 here. A twin box with 1793$^3$ each?} The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}. The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}. For dark matter and gas, the mass resolutions are $1.57\times 10^7~M_{\odot}$ and $3.14\times 10^6~M_{\odot}$, respectively. The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process~\citep{2005Natur.433..604D}. Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}. Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}.

@@

As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass.
We adopt this definition of stellar masses for all \red{larger-scale cosmological} simulations described in the following sections, \red{except for Horizon-AGN which use total mass (see Section~\ref{subsec:Horizon}) for details.}  Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure. Even more, the stellar mass using this 3D aperture can achieve good agreement to those measured within the Petrosian radii in observational studies~\citep{Schaye2015}. For further details of MBII simulation, we refer the reader to~\citet{Khandai2015}.

@@

The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback. In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy. For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at intervals between which the BH mass grows by a fixed fraction. \todo{Aklant: Referee asks: are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs? does it mean that the BH accretion is not modeled by the Bondi accretion between AGN feedback events?} \aklant{\bf{They are irregular simply because the BH mass growth is non- uniform. So it takes different amounts of time for the BH to grow by a fixed fraction. Bondi accretion is happening at all times. I have now removed the word `irregular' from this statement.}} The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency. Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN. As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy \red{stellar mass}. %, assuming a \cite{2003PASP..115..763C} IMF.

@@

The AGN feedback occurs in thermal, radio, and radiative modes. For high accretion rates, the feedback implementation is the same as Illustris i.e., thermal energy is injected in the surroundings of the accreting BHs. However, at low accretion rates, the feedback implementation is substantially different from Illustris. Instead of releasing hot bubbles, this feedback mode in TNG is purely kinetic. In particular, there is a directional injection of momentum along a randomly chosen direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W} at irregular intervals. The transition between the two feedback modes is also different from Illustris, and is set by the minimum value of 0.1 and $2 \times 10 ^{-3} \times (M_{BH} / 10^8~M_{\odot})$. Additionally, the radiative feedback implemented in Illustris~(summarized in the previous section) is also present in TNG. Lastly, the galaxy stellar mass in Illustris-TNG is obtained in a similar manner to that of Illustris.

@@

The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$. %A Salpeter IMF is assumed. 
\red{Stellar feedback} is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.

@@

We identify galaxies applying the AdaptaHOP structure finder \citep{Aubert+04,Tweed+09} to the star particle distribution.  Galaxies are identified using a local threshold of 178 times the average matter density, with the local density of individual particles calculated using the 20 nearest neighbours. Only galaxies with more than 50 particles are considered. \red{Identified with this approach, for Horizon-AGN, the adopted galaxy mass corresponds to the total stellar mass of a galaxy, which is different than the other hydrodynamic simulations (i.e., within a 3D 30~kpc spherical aperture). This definition of stellar mass is commonly used in Horizon-AGN, whose stellar mass function is known~\citep{2017MNRAS.467.4739K}} to be in good agreement with observations.
%\todo{Mention that the \smass.}

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[trim = 0mm 0mm 65mm 10mm, clip, height=0.4\textwidth]{HSC_selection_MBII.png}}
{\includegraphics[trim = 0mm 0mm 20mm 10mm, clip,height=0.4\textwidth]{HST_selection_MBII.png}}
\end{tabular}
\caption{\label{fig:selection}Demonstration of AGN selection using MBII. {\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles) \red{for sample at redshift $z=0.6$}. A matched HSC sample is shown by the orange data points. The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space. \red{Note that this is the first  step of the sample selection. We future use AGN magnitude cut to assure that the simulation sample present similar $L_{\rm bol}$ distribution (e.g., see Figure~\ref{fig:offsets_nochange}-left) and \mbh\ distribution with the observation. We then use the same \smass\ cut to collect the final sample.}
{\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample.
% For visual comparison between the HSC and HST selection, we show the region of the HST selection window in the left panel as dashed lines. % \todo{No mention of the redshift in Fig.2}
}
\end{figure*}

@@

\red{Comparing with} HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample. We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it \red{left}}). (2) The $i$-band magnitude of the AGN are bright (see Section~\ref{sec:hsc}). 
%The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude is required to be brighter than 20.5 mag and 22.0 mag, respectively.
\red{The specific selection is made as follows: a value of AGN $i$-band magnitude is selected to make the sample selection so that the $L_{\rm bol}$ distribution is similar to the observation (see Section~\ref{sec:dis} for details). }
Since the simulations do not provide the observed AGN magnitude, we adopt a simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
 3)~Following the HSC selection, we require the \smass\ value to be above a certain level (according to their redshift) to assure an accurate measurement. Finally, the HSC sample is split into three redshift bins for making comparison which are $0.2<z<0.4$, $0.4<z<0.6$, and $0.6<z<0.8$.

\red{Comparing with} HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example). Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., \red{log(\mbh)} between [7.7, 8.6] $M_{\odot}$). The HST sample covers the higher redshift range $1.2<z<1.7$, which is considered as a single redshift bin to make the comparison with the simulations at $z=1.5$.

@@

\section{Results} \label{sec:result}
%\todo{Explain the offset depends.}
\red{For comparison purpose, the local scaling relation introduced by D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF based\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion. This local relation is derived by fitting the \mbh-\smass\ relations using 55 local galaxies by~\citet{Bennert++2011} and \citet{H+R04}, in which \smass\ measurements are Chabrier IMF based.}
\red{For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the $y$-axis) and calculating their mean and the standard deviation to make comparisons with the observation.}

\red{In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison. For the simulation data, both the initial sample and the ones after observational effect (i.e., inject observational noise correction, and apply equivalent selection) are show in the figure. 
Note that there are three types of offset value that can be collected for the simulation sample: the initial offset, the offset with selection effect, and the offset with noise injection and selection effect. For the initial offset, it has been known~\citep[e.g.,][Figure 2]{Habouzit2021} and can be seen in Figure~\ref{fig:comparsion} that the initial offset values vary at different stellar mass range, and thus the mean and standard derivation could not represent the entire distribution.}
\red{In this work, we focus on the other two offset value distributions, i.e., considering selection effect but with/without noise correction. To aid in visualization of the differences among the various simulations compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.  Each panel presents a different redshift range. In addition, the values of the central offset and scatter for before and after considering the noise are presented in Table~\ref{tab:sum}. The interpolations and the comparison with the observations are presented in the rest of this section.}

>>>>

\section{Introduction} \label{sec:intro}
The close correlations between \red{the mass of} supermassive black holes (\red{\mbh}) and the properties of their host galaxies (e.g., stellar mass\red{, \smass}) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}. To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over \red{cosmic time}. While, an {\it observed} evolution has been found \red{since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15} in} which the growth of BHs predates that of the host, other studies \red{\citep[e.g.,][]{Schramm2013, Sun2015} predict that} BHs grow commensurately with galaxies.
However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009,  Ding2020,Li2021b}.

@@

To avoid any potential biases related to the selection of the quasars, \citet{Li2021b} isolated 877 sources which are uniformly selected based on their PSF-magnitudes, color cuts using single-epoch SDSS photometry and the value of the measured \smass. Specifically, we use the {\it ugri} color-selected sample (228 sources) from SDSS I/II~\citep{Richards2002}, and the CORE sample from SDSS BOSS (408 sources) and eBOSS (241 sources) surveys~\citep{Ross2013, Myers2015} (hereafter the uniform sample). These samples are initially selected based on PSF-magnitude cuts of $15 < i < 19.1$ (for {\it ugri}), and $i > 17.8$ and $g, r < 22.0$ (for CORE). Furthermore, a limit on \smass\ is set to assure the detection of the host, especially since the rate and accuracy of detection is higher when \smass\ is increasing, resulting in a final sample of 646 quasars. These selections will be adopted in an equivalent manner to the simulated samples to mitigate selection effects thus allowing the fair comparison.

@@

The measurements of the \mbh-\smass\ relations for both the HST and HSC samples are obtained with a consistent approach. Thus, we expect the measurement errors of these two samples to be at a comparable level (i.e., $\Delta$\mbh$=0.4~$dex, $\Delta$\smass$=0.2~$dex). 
Indeed, the two samples are consistent with a lack of evolution in the mass ratio~\citep[see Figure 6 of][]{Li2021b}, even though the sample selection is slightly different.

\begin{deluxetable*}{lccccc}
\tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} & MBII & Illustris &  TNG100 & TNG300 & Horizon-AGN
}
\startdata
box sizes $(\mathrm{cMpc})^3$  & $142.7^3$ & $(106.5)^3$ & $(111)^3$ & $(302)^3$ & $(142)^3$ \\
particles  & $2\times1792^3$ & $2\times1820^3$ & $2\times1820^3$ & $2\times2500^3$ & $\sim2\times1024^3$ \\
\cline{1-6}
{\bf mass resolution} \\
 dark matter &$1.57\times10^7$ & $6.26\times10^6$ & $7.5\times10^6$ & $5.9\times10^7$ & $8\times10^7$ \\
 baryonic matter &$3.14\times10^6$ & $1.26\times10^6$ & $1.4\times10^6$ & $1.1\times10^7$ & $2\times10^6$ \\
\cline{1-6}
{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ \red{radiative efficiency})} \\
High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
Low acc. mode  & -- & 0.35 $\times$ 0.2 & $\leq0.2 \times$ 0.2 & $\leq0.2 \times$ 0.2 & 1 $\times$ 0.1 \\
Transitions btw. modes & -- & 0.05 & \multicolumn{2}{c}{min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%]} & 0.01 \\
\cline{1-6}
AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & $\dot{M}_{Bondi}$&$\dot{M}_{Bondi}$ & $\alpha\dot{M}_{Bondi}$ \\
maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
\enddata
\tablecomments{In the penultimate row, $\alpha$ is the boost factor. For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$[(\rho/\rho_0)^2, 1]$. $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$.
\red{The `$\leq$' sign in the low accretion feedback mode of TNG means that the feedback efficiency follows a distribution with a maximum value of 0.2. Note that the radiative efficiencies are different in various simulations. Thus, different values are used for calculating the luminosity.}
%\todo{Aklant: The $\leq$ sign in the low accretion feedback mode of TNG is also not clear. Is it a fixed value or a distribution?}\aklant{[\bf{It just means that the efficiency is actually function (not a constant) but the maximum value is 0.2}]} 
%\todo{Aklant: Referee asks us whether the same radiative efficiency is used to compute AGN luminosity in all the simulations. But we already show these values in Table 1, which are different, don't we?} \aklant{\bf{Yes the radiative efficiencies are different in the different simulations, and we use these different values for the computing the luminosities in each case. This is true at least for the simulations that I provided to you.}}
}
\end{deluxetable*}

\section{Simulations and comparison strategy}
%\todo{Uniform the descriptions of the simulations to lack homogeneity. (Illustris has star formation threshold). Re-write the section and provide the same information}
\label{sec:simulations}
We introduce the simulation samples that are adopted in this study. All are based on larger-scale cosmological simulations, except the Semianalytic Model (SAM; see Section~\ref{subsec:SAM}). In Table~\ref{tab:sim_sum}, we summarized the key elements for each hydrodynamic simulation being considered. \red{We note that each simulation adopts either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} IMF. To make self-consistent comparisons, we ensure that the adopted IMF for both the simulations and the observations are consistent. The assumed IMF is needed to obtain the mass-to-light ratio and convert the observed luminosity to stellar mass to perform the comparisons. For numerical simulation, the mass is the base material which is IMF independent.}

\subsection{{\tt MassiveBlackII} (MBII)}\label{subsec:MBII}
MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $(142.7~\mathrm{cMpc})^3$
and $2\times1792^3$~\red{(i.e., dark matter + gas)} particles. 
%\todo{Aklant: Please answer what is the factor 2 here. A twin box with 1793$^3$ each?\aklant{\bf{The 2 represents that there are $1792^3$ DM particles and $1792^3$ gas particles}}} 
The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}. The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}. For dark matter and gas, the mass resolutions are $1.57\times 10^7~M_{\odot}$ and $3.14\times 10^6~M_{\odot}$, respectively. The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process~\citep{2005Natur.433..604D}.

@@

Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}. Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}. As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass.
We adopt this definition of stellar masses for all \red{larger-scale cosmological} simulations described in the following sections, \red{except for Horizon-AGN which use total mass (see Section~\ref{subsec:Horizon}) for details.}  Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure. Even more, the stellar mass using this 3D aperture can achieve good agreement to those measured within the Petrosian radii in observational studies~\citep{Schaye2015}. For further details of MBII simulation, we refer the reader to~\citet{Khandai2015}.

@@

The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback. In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy. For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at \red{the} intervals between which the BH mass grows by a fixed fraction. 
(%\todo{Aklant: Referee asks: are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs? does it mean that the BH accretion is not modeled by the Bondi accretion between AGN feedback events?} \aklant{\bf{They are irregular simply because the BH mass growth is non- uniform. So it takes different amounts of time for the BH to grow by a fixed fraction. Bondi accretion is happening at all times. I have now removed the word `irregular' from this statement.}} 
The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency. Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN. \aklant{Halos and galaxies are identified similar to that of MBII}. As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy \red{stellar mass}. %, assuming a \cite{2003PASP..115..763C} IMF.

@@

The AGN feedback occurs in thermal, radio, and radiative modes. For high accretion rates, the feedback implementation is the same as Illustris i.e., thermal energy is injected in the surroundings of the accreting BHs. However, at low accretion rates, the feedback implementation is substantially different from Illustris. Instead of releasing hot bubbles, this feedback mode in TNG is purely kinetic. In particular, there is a directional injection of momentum along a randomly \red{chosen direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W}}. % at irregular intervals. 
The transition between the two feedback modes is also different from Illustris, and is set by the minimum value of 0.1 and $2 \times 10 ^{-3} \times (M_{BH} / 10^8~M_{\odot})$. Additionally, the radiative feedback implemented in Illustris~(summarized in the previous section) is also present in TNG. Lastly, \aklant{halo and galaxy identification, as well as calculation of galaxy stellar mass, is done in a similar manner to that of Illustris and MBII}.

@@

%The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$. %A Salpeter IMF is assumed. 
%\red{Stellar feedback} is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.

@@

We identify galaxies applying the AdaptaHOP structure finder \citep{Aubert+04,Tweed+09} to the star particle distribution.  Galaxies are identified using a local threshold of 178 times the average matter density, with the local density of individual particles calculated using the 20 nearest neighbours. Only galaxies with more than 50 particles are considered. \red{With this approach for Horizon-AGN, the adopted galaxy mass corresponds to the total stellar mass of a galaxy, which is different than the other hydrodynamic simulations (i.e., within a 3D 30~kpc spherical aperture). This definition of stellar mass is commonly used in Horizon-AGN, whose stellar mass function is known~\citep{2017MNRAS.467.4739K}} to be in good agreement with observations.
%\todo{Mention that the \smass.}

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[trim = 0mm 0mm 65mm 10mm, clip, height=0.4\textwidth]{HSC_selection_MBII.png}}
{\includegraphics[trim = 0mm 0mm 20mm 10mm, clip,height=0.4\textwidth]{HST_selection_MBII.png}}
\end{tabular}
\caption{\label{fig:selection}Demonstration of AGN selection using MBII. {\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles) \red{for those at redshift $z=0.6$}. A matched HSC sample is shown by the orange data points. The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space. \red{Note that this is the first step of sample selection. We further use an AGN magnitude cut to assure that the simulation sample has a similar $L_{\rm bol}$ distribution (e.g., see Figure~\ref{fig:offsets_nochange}-left) and \mbh\ distribution with the observations. We then use the same \smass\ cut to construct the final sample.}
{\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample.
% For visual comparison between the HSC and HST selection, we show the region of the HST selection window in the left panel as dashed lines. % \todo{No mention of the redshift in Fig.2}
}
\end{figure*}

@@

\red{Comparing with} the HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample. We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it \red{left}}). (2) The $i$-band magnitude of the AGN are bright (see Section~\ref{sec:hsc}). 
%The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude is required to be brighter than 20.5 mag and 22.0 mag, respectively.
\red{The specific selection is carried out as follows: a value of AGN $i$-band magnitude is chosen to make the sample selection such that the $L_{\rm bol}$ distribution is similar to the observations (see Section~\ref{sec:dis} for details). }
Since the simulations do not provide the observed AGN magnitude, we adopt a simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
 3)~Following the HSC selection, we require the \smass\ value to be above a certain level (according to their redshift) to assure an accurate measurement. Finally, the HSC sample is split into three redshift bins for making comparison which are $0.2<z<0.4$, $0.4<z<0.6$, and $0.6<z<0.8$.

\red{Comparing with} the HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example). Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., \red{log(\mbh)} between [7.7, 8.6] $M_{\odot}$). The HST sample covers the higher redshift range $1.2<z<1.7$, which is considered as a single redshift bin to make the comparison with the simulations at $z=1.5$.

@@

\section{Results} \label{sec:result}
%\todo{Explain the offset depends.}
\red{For comparison, the local scaling relation provided by  D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion \blue{with redshift}. This local relation \blue{(\mbh-\smass\))} is derived by \blue{fitting measurements for} 55 local galaxies as given in~\citet{Bennert++2011} and \citet{H+R04}.
%, in which \smass\ measurements are Chabrier IMF based.
}
\red{For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the $y$-axis) and calculate their mean and standard deviation to make comparisons with observations.}

\red{In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison. For the simulated data, both the initial sample and that with observational effects applied (i.e., noise correction, and selection) are shown. Note that \blue{offsets can occur for the simulated sample in three cases}: an \blue{inherent} offset, an offset due to selection, and offsets from added noise and selection. For the first, it has been recognized~\citep[e.g.,][Figure 2]{Habouzit2021}, and seen in Figure~\ref{fig:comparsion}, that the  offset values \blue{vary over a range of} stellar mass, and thus the mean and standard derivation do not represent the entire mass distribution.}
\red{In this work, we focus on the latter two offset distributions, i.e., considering selection effects with and without noise correction. To aid in visualization of the differences among the various simulations, compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.  Each panel presents a different redshift range. In addition, the values of the central offset and scatter are presented 
in Table~\ref{tab:sum}, both before and after consideration of the noise. \blue{Comparisons with the} observations are presented in the remainder of this section.}

\begin{figure*}
\centering
\includegraphics[trim = 40mm 60mm 30mm 90mm, clip,height=1.1\textwidth]{MM_sum.png}
\caption{\label{fig:comparsion} 
Black hole mass versus stellar mass for both the observational (small orange circles) and simulated (small colored circles) samples. Each row pertains to a particular simulation as labelled. The panels, from left to right, show different redshift bins. The black line in each panel indicates the local relation adopted by~\citet{Ding2020}. The background cloud (in green and yellow \red{with contours}) shows the intrinsic simulation number density before injecting random noise and applying selection effects. \red{The TNG100 and TNG300 appear to present similar results (see discussion section)}.
}
\end{figure*}
